Personality and political beliefs across the lifespan

### 2019-11-20 scripts/manuscript.Rmd
added table 1 of personality traits across age groups

```
# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

>>>>

```{r table1, echo = FALSE, results = "asis"}
tidy_table <- tidy %>% 
  mutate(age = case_when(       
      age <= 30 & age >= 20 ~ "[20-30]",
      age <= 40 & age >= 31 ~ "[31-40]",
      age <= 50 & age >= 41 ~ "[41-50]",
      age <= 60 & age >= 51 ~ "[51-60]",
      TRUE ~ "[61-68]"))
tidy_table <- tidy_table %>% 
  group_by(personality_trait, age) %>% 
  summarize(mean_personality_score = mean(personality_score)) %>% 
  pivot_wider(names_from = age, values_from = mean_personality_score) %>% 
  rename("Personality Trait" = personality_trait)

apa_table(tidy_table, 
            caption = "Mean Personality Trait Scores Across the Lifespan",
          col_spanners = list(`Age Group` = c(2, 6)),
          note = "Personality trait scores reported on a 1-7 scale."
)
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
